### 2015-04-28 paper/preamble.tex
Move page and table commands out of the preamble to allow externalized generation

\usepackage{pdflscape}
\usepackage{geometry}

\newenvironment{wide}{
\pagebreak
\newgeometry{
 top=15mm,
 inner=15mm,
 outer=15mm,
 bottom=15mm,
 headheight=15pt,
 headsep=5mm,
 footnotesep=5mm,
 footskip=10mm}
\begin{landscape}
% Use TiKZ?
% http://tex.stackexchange.com/questions/40501/using-restoregeometry-in-environment-next-page-runs-off-the-page-bottom/40503#40503
\setlength\LTleft{0pt}            % default: \fill
\setlength\LTright{0pt}           % default: \fill
}{
\end{landscape}
\pagebreak
\aftergroup\restoregeometry
}

\newenvironment{portraitdatapage}{
\pagebreak
\newgeometry{
 top=15mm,
 inner=15mm,
 outer=15mm,
 bottom=15mm,
 headheight=15pt,
 headsep=5mm,
 footnotesep=5mm,
 footskip=10mm}
% Use TiKZ?
% http://tex.stackexchange.com/questions/40501/using-restoregeometry-in-environment-next-page-runs-off-the-page-bottom/40503#40503
\setlength\LTleft{0pt}            % default: \fill
\setlength\LTright{0pt}           % default: \fill
}{
\pagebreak
\aftergroup\restoregeometry
}

@@

\usepackage{longtable}
\setlength\LTcapwidth{\textwidth} % default: 4in (rather less than \textwidth...)

\usepackage{caption}
\usepackage{pgfplotstable}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{array}
\pgfplotsset{compat=1.11}% supress warning

\pgfplotstableset{
% Write all longtable tables to disk.
every table/.append style={outfile={.generated.report-table\@arabic\c@LT@tables.tex}},
% Use cached/written files as input.
include outfiles,
% Change to true to force re-generation. It's easier to just delete all generated files.
% force remake=true,
}

\newcolumntype{i}{>{\begin{pgfplotstablecoltype}[int detect]}r<{\end{pgfplotstablecoltype}}}
\newcolumntype{f}{>{\begin{pgfplotstablecoltype}[fixed zerofill]}r<{\end{pgfplotstablecoltype}}}
\newcolumntype{t}{>{\arraybackslash}p{.3\linewidth}}
\newcolumntype{T}{>{\arraybackslash}p{.9\linewidth}}

% TODO: reduce code-duplication between \tsvtablestyle/wide/widedatasets/superwidedatasets
\newcommand{\tsvtablestyle}[0]{
\pgfplotstableset{
format=file,
col sep=tab,
multicolumn names={c},
column type=r,
int detect,
zerofill=true,
precision=3,
1000 sep={\ },
begin table=\begin{longtable*},
end table=\end{longtable*},
every odd row/.style={before row={\rowcolor[gray]{0.95}}},
every head row/.style={before row=\toprule,after row={
\toprule
\addlinespace[0pt]
\endhead
},
},
every last row/.style={after row={
\bottomrule
}
},
}
}

\newcommand{\tsvtable}[3]{
\tsvtablestyle
\pgfplotstabletypeset[
columns={#2},#3
]{#1}
}

\newcommand{\tsvtablestylewide}[1]{
\pgfplotstableset{
format=file,
col sep=tab,
multicolumn names={c},
column type=r,
int detect,
zerofill=true,
precision=3,
1000 sep={\ },
begin table=\begin{longtable},
end table=\end{longtable},
every odd row/.style={before row={\rowcolor[gray]{0.95}}},
every head row/.style={before row=\toprule,after row={
\toprule
\addlinespace[0pt]
\endhead
},
},
every last row/.style={after row={
\bottomrule
\caption{#1}}
},
}
}

\newcommand{\tsvtablewide}[4]{
\tsvtablestylewide{#2}
\pgfplotstabletypeset[
columns={#3},#4
]{#1}
}

\newcommand{\tsvtablewidedatasets}[4]{
\tsvtablestylewide{#2}
\pgfplotstabletypeset[
columns={#3},every nth row={4[-1]}{after row={\addlinespace[0pt]\midrule\addlinespace[0pt]}},fixed,display columns/0/.style={string type, column type=l},display columns/1/.style={string type, column type=i|},#4
]{#1}
}

\newcommand{\tsvtablesuperwidedatasets}[4]{
\tsvtablestylewide{#2}
\pgfplotstabletypeset[
columns={#3},every nth row={4[-1]}{after row={\addlinespace[0pt]\midrule\addlinespace[0pt]}},fixed,display columns/0/.style={string type, column type=l},display columns/1/.style={string type, column type=i|},%
% Remove dataset dates.
display columns/0/.append style={string replace*={2014-09-01.}{}},%
display columns/0/.append style={string replace*={2014-08-29.}{}},%
display columns/0/.append style={string replace*={2014-07-23.}{}},%
display columns/0/.append style={string replace*={2014w35.}{}},%
display columns/0/.append style={string replace*={2014-07-10.}{}},%
% Shorten health status datasets.
display columns/0/.append style={string replace*={healthstatus.2013.}{hs.}},%
display columns/0/.append style={string replace*={.domain-registrars}{.registrars}},%
display columns/0/.append style={string replace*={.financial-services}{.financial}},%
display columns/0/.append style={string replace*={.higher-education}{.education}},%
display columns/0/.append style={string replace*={.public-authorities}{.pubauth}},%
% Shorten dataset counts.
display columns/0/.append style={string replace*={100000}{100k}},%
display columns/0/.append style={string replace*={10000}{10k}},%
% Shorten Alexa datasets.
display columns/0/.append style={string replace*={alexa.top.se.10k.}{alexa.top.se.}},%
display columns/0/.append style={string replace*={alexa.top.dk.10k.}{alexa.top.dk.}},%
% Shorten dataset type.
display columns/0/.append style={string replace*={random.}{rnd.}},%
display columns/0/.append style={string replace*={-https-www}{-sw}},%
display columns/0/.append style={string replace*={-https}{-s}},%
display columns/0/.append style={string replace*={-http-www}{-hw}},%
display columns/0/.append style={string replace*={-http}{-h}},%
,#4
]{#1}
}

@@

\usepackage[pfx=.generated.]{jpfigurecommands}

>>>>

@@

@@

\usepackage{jppagecommands}
\usepackage[pfx=.generated.paper-]{jptablecommands}
\usepackage[pfx=.generated.]{jpfigurecommands}
